---
title: "Visual representation of paleogeoscientific data"
author: "Simon Goring"
date: "April 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PaleoVisualization Background.

### Data Access

#### Visualization Representation

This sheet contains a number of columns, intended to represent 

```{r, echo = TRUE, warning=FALSE, message=FALSE, results='hide'}
library(dplyr)

source('R/file_download.R')
testing <- try(pull_sheets("Visualization Representation"))

```

##### Current Issues

We want all of the subsequent check-boxes to be checked.  

  * `r ifelse(any(stringr::str_detect(colnames(testing), "^X\\d")), "&#x2610;", "&#x2611;")` No unnamed columns are being imported.
  * `r ifelse(any(rowSums(!is.na(testing))==0), "&#x2610;", "&#x2611;")` All rows contain at least one entry.
  * `r ifelse(!any(duplicated(testing[,1:2])), "&#x2610;", "&#x2611;")` The first two columns represent the data unique key.
  * `r ifelse(!any(duplicated(testing[,1:2])), "&#x2610;", "&#x2611;")` The first two columns represent the data unique key.

  
#### Data Output

Current data structure:

```{r, echo = FALSE}

DT::datatable(testing)

```